% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments
First and foremost, I would like to thank my supervisors, Dr. Robert Mart\'i, Prof. Fabrice M\'eriaudeau, Dr. Jordi Freixenet, and Dr. Paul Walker for their constant support and guidance through this thesis.
%% I would like to reiterate an additional thanks to Bobby and Fab for their ability to believe in me --- at least I hope so --- and push me further even while I am very late, getting sidetrack, or enjoying coffee and for being friends over those years.
I would like to reiterate an additional thanks to Bobby and Fab for their ability to believe in me --- at least I hope so --- and push me further even while I am very late and getting sidetrack.
Thanks for being friends over those years.
I enjoyed every minute of our scientific discussions, barbecue dinner, and unfinished nightly frozen trails as well as unfinished sweltering Alpine ride (unfinished apply to me usually).
Without you this work would not simply be what it is. 

Thanks to D\'esir\'e Sidib\'e as well for sharing his valuable knowledge and ideas.
I would like thank Dr. Joan Vilanova for his precious help to collect and annotate data as well as guiding me through the understanding of all those MRI modalities.

Thanks to C\'edric Demonceaux, Olivier Morel, Josep Quintana, and Joan Massich for our training sessions during the past years.
Lets check Strava in two months from now.
And of course thanks to all my friends: Abir, Armine, Cansen, David, DP, Fran\c{c}ois, Amanda, Konstantin, Habib, Sarah, Sharad, Josep, Sergi, Mireia, Sonia, Shihav, and last but not least Sik for our endless scientific related discussions, ideas, excitements, and disappointments.
I enjoyed all of our discussions.

Special thanks to Joseta, Aina, Montse, Mireia, and Nathalie for their constant and patient help with my endless paperwork, mission order, enrolment, and questions.

I also would like to thank Prof. Su Ruan and Prof. Reyer Zwiggelaar to have accepted to review the present manuscript.
I would also like to acknowledge AGAUR FI-DGR 2012 grant, provided by the Autonomous Government of Catalunia which is the sole reason for existence of this thesis.
It is an honored to be among its holders.

Last but not least, I would like to thank my family that has always being there for me with their endless love and support, my parents, Ginette and Patrice, my brother, C\'edric and his family, V\'eronique, Julian, and Sarah.
I would like to thank the family of my wife, although being far away I appreciate your concerns and supports. 

Finally I would like to express my most sincere gratitude to my wife, Mojdeh, for her love, happiness, kindness among other qualities.
Without her this manuscript would not be written.
   

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------


