\begin{publication}

\subsubsection*{Peer-Review Journals Papers}

\begin{enumerate}\scriptsize
\item \textbf{G. Lemaitre, R. Marti, M. Rastgoo, J. Massich, F. Freixenet, J. C. Vilanova, and F. Meriaudeau}, ``Automatic prostate cancer detection through DCE-MRI images: all you need is a good normalization'', \textit{Medical Image Analysis}, Submitted.
\item \textbf{G. Lemaitre, F. Nogueira, and C. Aridas}, ``Imbalanced-learn: A Python Toolbox to Tackle the Curse of Imbalanced Datasets in Machine Learning'', \textit{Journal of Machine Learning Research}, Submitted.
\item \textbf{G. Lemaitre, M. Rastgoo, J. Massich, C. Y. Cheung, T. Y. Wong, E. Lamoureux, D. Milea, F. Meriaudeau, and D. Sidibe}, ``Classification of SD-OCT Volumes using Local Binary Patterns: Experimental Validation for DME detection'', \textit{Journal of Ophthalmology}, vol. 2016, May 2016.
\item \textbf{G. Lemaitre, R. Marti, J. Freixenet, J. C. Vilanova, P. M. Walker, and F. Meriaudeau}, ``Computer-Aided Detection and Diagnosis for prostate cancer based on mono and multi-parametric MRI: A Review'', \textit{Computer in Biology and Medicine}, vol. 60, pp 8 - 31, 2015.
\end{enumerate}

\subsubsection*{Peer-Review International Conferences}

\begin{enumerate}\scriptsize
\item \textbf{G. Lemaitre, M. Rastgoo, J. Massich, J. C. Vilanova, P. M. Walker, J. Freixenet, A. Meyer-Baese, F. Meriaudeau, and R. Marti}, ``Normalization of T2W-MRI prostate images using Rician a priori'', \textit{SPIE Medical Imaging 2016}. San Diego: USA (February 2016).
\item \textbf{G. Lemaitre, M. Rastgoo, J. Massich, S. Sankar, F. Meriaudeau, and D. Sidibe}, ``Classification of SD-OCT volumes with LBP: Application to DME detection'', \textit{Ophthalmic Medical Image Analysis Workshop (OMIA), Medical Image Computing and Computer Assisted Interventions (MICCAI) 2015}. Munich: Germany (Oct. 2015).
\item \textbf{G. Lemaitre, J. Massich, R. Marti, J. Freixenet, J. C. Vilanova, P. M. Walker, D. Sidibe, and F. Meriaudeau}, ``A Boosting Approach for Prostate Cancer Detection using Multi-parametric MRI'', \textit{International Conference on Quality Control and Artificial Vision (QCAV) 2015}. Le Creusot: France (Jun. 2015).
\item \textbf{G. Lemaitre, A. Bikfalvi, J. Llach, J. Massich, and F. Julian}, ``Business Model Design for University Technology Valorisation'', \textit{International Technology, Education and Development Conference (INTED) 2015}. Madrid: Spain (Mar. 2015).
\end{enumerate}

\subsubsection*{Thesis}

\begin{enumerate}\scriptsize
\item \textbf{G. Lemaitre, A. Bikfalvi, and J. Llach}, ``Valorisation of Computerized Technology in the Health Care Sector'', \textit{Thesis for Master in Science Business Innovation and Technology Management (BITM)}, 2014.
\end{enumerate}

\subsubsection*{Contributed Peer-Review Journals Papers}

\begin{enumerate}\scriptsize
\item \textbf{K. Alsaih, G. Lemaitre, J. Massich, M. Rastgoo, D. Sidibe, and F. Meriaudeau}, ``Machine Learning Techniques for DME Classification on SD-OCT images'', \textit{BioMedical Engineering OnLine}, Submitted.
\item \textbf{I. P. Houben, P. Van de Voorde, C. R. Jeukens, J. E. Wildberger, G. Lemaitre, I. A. Illan, A. Meyer-Baese, L. F. Kooreman, M. L. Smidt, and M. B. Lobbes}, ``Contrast-enhanced spectral mammography as work-up tool in patients recalled from breast cancer screening: risks versus benefits'', \textit{European Radiology}, Submitted.
\item \textbf{D. Sidibe, S. Sankar, G. Lemaitre, M. Rastgoo, J. Massich, C. Y. Cheung, G. S. Tan, D. Milea, E. Lamoureux, T. Y. Wong, and F. Meriaudeau}, ``An anomaly detection approach for the identification of DME patients using spectral domain optical coherence tomography images'', \textit{Computer Methods and Programs in Biomedicine}, Submitted.
\item \textbf{M. Belkacemi, C. Stolz, A. Mathieu, G. Lemaitre, J. Massich, and O. Aubreton}, ``Non Destructive Testing based on a Scanning-From-Heating approach: Application to non-through Defect Detection and Fiber Orientation Assessment'', \textit{Journal of Electronic Imaging}, vol. 24(6), pp 1-8, Nov/Dec 2015.
\end{enumerate}

\subsubsection*{Contributed Peer-Review International Conferences Papers}

\begin{enumerate}\scriptsize
\item \textbf{J. Massich, M. Rastgoo, G. Lemaitre, C. Cheung, T. Y. Wong, D. Sidibe, and F. Meriaudeau}, ``Classifying DME vs normal SD-OCT volumes: A review'', \textit{23\textsuperscript{rd} International Conference on Pattern Recognition (ICPR) 2016}. Cancun: Mexico (December 2016).
\item \textbf{K. Alsaih, G. Lemaitre, J. Massich, M. Rastgoo, D. Sidibe, T. Y. Wong, E. Lamoureux, D. Milea, C. Leung, and F. Meriaudeau}, ``Classification of SD-OCT volumes with multi-pyramids, LBP and HoG descriptors: Application to DME detection'', \textit{38\textsuperscript{th} International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) 2016}. Orlando: USA (August 2016).
\item \textbf{A. Pampouchidou, K. Marias, M. Tsiknakis, P. Simos, F. Yang, G. Lemaitre, and F. Meriaudeau}, ``Video-based depression detection using local curvelet binary patterns in pairwise orthogonal planes'', \textit{38\textsuperscript{th} International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC) 2016}. Orlando: USA (August 2016).
\item \textbf{S. Hoffmann, M. Lobbes, I. Houben, K. Pinker-Domenig, G. Wengert, B. Burgeth, U. Meyer-Baese, G. Lemaitre, and A. Meyer-Baese}, ``Computer-aided diagnosis of diagnostically challenging lesions in breast MRI: a comparison between a radiomics and a feature-selective approach'', \textit{SPIE Commercial+ Scientific Sensing and Imaging}. Baltimore: USA (July 2016).
\item \textbf{M. Belkacemi, C. Stolz, A. Mathieu, G. Lemaitre, and O. Aubreton}, ``A combined three-dimensional digitisation and subsurface defect detection data using active infrared thermography'', \textit{13\textsuperscript{th} Quantitative Infrared Thermography Conference (QIRT)}. Gdansk: Poland (July 2016).
\item \textbf{M. Belkacemi, J. Massich, G. Lemaitre, C. Stolz, V. Daval, G. Pot, O. Aubreton, R. Collet, and F. Meriaudeau}, ``Wood fiber orientation assessment based on punctual laser beam excitation: A preliminary study'', \textit{13\textsuperscript{th} Quantitative Infrared Thermography Conference (QIRT)}. Gdansk: Poland (July 2016).
\item \textbf{M. Rastgoo, G. Lemaitre, J. Massich, O. Morel, F. Marzani, R. Garcia, and F. Meriaudeau}, ``Study of Data Imbalancing for Melanoma Classification'', \textit{3\textsuperscript{rd} International Conference on BIOIMAGING}. Rome: Italy (February 2016).
\item \textbf{M. Rastgoo, G. Lemaitre, O. Morel, J. Massich, F. Marzani, R. Garcia, and D. Sidibe}, ``Classification of melanoma lesions using sparse coded features and random forests'', \textit{SPIE Medical Imaging 2016}. San Diego: USA (February 2016).
\item \textbf{A. Meyer-Baese, J. Massich, G. Lemaitre, and M. Rastgoo}, ``Real-Time Optical Flow with Theoretically Justified Warping Applied to Medical Imaging'', \textit{Breast Image Analysis Workshop (BIA), Medical Image Computing and Computer Assisted Interventions (MICCAI) 2015}. Munich: Germany (Oct. 2015).
\item \textbf{J. Massich, G. Lemaitre, J. Marti and F. Meriaudeau}, ``An Optimization Approach to Segment Breast Lesions in Ultra-Sound Images using Clinically Validated Visual Cues'', \textit{Breast Image Analysis Workshop (BIA), Medical Image Computing and Computer Assisted Interventions (MICCAI) 2015}. Munich: Germany (Oct. 2015).
\item \textbf{J. Massich, G. Lemaitre, J. Marti, and F. Meriaudeau}, ``Brest Ultra-Sound image Segmentation: an Optimization approach based on super-pixels and high-level descriptors'', \textit{International Conference on Quality Control and Artificial Vision (QCAV) 2015}. Le Creusot: France (Jun. 2015).
\end{enumerate}

\end{publication}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
